---
title: "Gapminder Analysis"
author: "Calla Bush St George"
date: "`r Sys.Date()`"
output: 
  html_document:
      toc: yes
      toc_float: yes
      code_folding: hide
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the first line of my document. In this document, I will analyze
how life expectancy has changed over time.

# Reading in Gapminder data

```{r reading in data}
gapminder_df <- read.csv("Data/gapminder_data.csv")

```

## Smaller header

### Even smaller header

##### Very small header

Lists: \* List item 1 \* List item 2

Another type of list: - Hyphen list - Hyphen list

Numbered list: 1. Number one 2. Number two \* Sub list 3. Number 3

We make text **bold with two asterisks** or *italic with one asterisk*

We can also insert Greek letters with $\mu$ or $\Delta$ .

We can make hyperlinks [bluewords](etherpadlink)

# Calculating summary statistics

```{r Calculating-median-pop, echo=FALSE}
med_pop <- median(gapminder_df$pop)

num_obs <- nrow(gapminder_df)
```

Over `r num_obs` observations, the median population was
`r round(med_pop/10e6)` million people

#Installing nationalparkcolors package

```{r install nationalparkscolors}
#install.packages("devtools")
devtools::install_github("katiejolly/nationalparkcolors")
install.packages("wesanderson")
```

# Plotting life expectancy over the years

```{r Line Graph, warning = FALSE}
library(nationalparkcolors)
library(wesanderson)
library(ggplot2)
pal <- park_palette("SmokyMountains",5)
ggplot(gapminder_df, aes(x = year, y = lifeExp, group = country, color = continent)) +
  geom_smooth() + scale_y_log10() + scale_x_continuous(limits = c(1997, 2007))

```

#Plotting population distribution

```{r histogram, message = FALSE, fig.width = 10}
ggplot(gapminder_df, aes(x = pop)) +
  geom_histogram()
```

Add new lines cause now we are working in git
